---
title: "Precipitation Analysis"
author: "Alex Bans"
date: "today"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Insert background info about station here. 

## Summary

## Background

## Future Updates
  There are several ideas in the works about how to improve this report. These include: adding in temperature data, long term precipitation data from NOAA, and statistical analysis (including return intervals). Additionally, we will potentially be working on gathering data from all the other hydra gauges in the network to determine the differences in rain spatially in the Portland Metro area, and how much estimated volume of flow was produced per storm event. Finally, we will be working on automating the generation of this report and automating sharing these results via email. Interested parties will be able to sign up via GoogleDocs and specify the interval in which they want the results. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
